Combined annotation exploration for SCPCP000006

### 2024-11-01 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
render final notebook

- Combining label transfer and CNV inference we annotated 38/40 Wilms tumor samples in SCPCP000006. For the two remaining samples, we need to investigate inferCNV further:
    - SCPCS000190 only has 1 normal cell, so we cannot specify a reference for inferCNV
    - SCPCS000203 does not run properly through inferCNV; cells are removed from the inferCNV inference, and why requires further investigation

>>>>

- Combining label transfer and CNV inference we annotated 38/40 Wilms tumor samples in SCPCP000006. For the two remaining samples, we need to investigate inferCNV further:
    - SCPCS000190 only has 1 normal cell, which is insuffient as a reference for inferCNV
    - SCPCS000203 does not run properly through inferCNV; cells are removed from the inferCNV inference, and why requires further investigation
